The goal of this analysis is to identify the number of subjects we would need to reliably detect a null correlation between complexity and optimality, measured as distance from the optimal bound. We will do this using data from [Filipowicz et al., 2020](https://elifesciences.org/articles/57872), which contains examples of the conditions we are trying to replicate/

Load correlations for low and high hazard in auditory 2 alternative forced choice data (A2AFC data)
```{r}
adat = read.csv('.../data/A2AFC_PI.csv')
adat$Hazard = factor(adat$Hazard,labels=c('H=0.01','H=0.99'))
```

Plot correlations
```{r}
library(ggplot2)

ggplot(adat,aes(Ipast,DFB,fill=Hazard))+
  geom_point(size=3,shape=21,color='white')+
  geom_smooth(method='lm',se=F,color='black')+
  facet_wrap(~Hazard)+
  scale_fill_manual(values=c('blue','orange'))+
  ylab('Distance from Optimal Bound')+
  xlab('Complexity (Ipast)')
```

Use BRMS to get regression coefficients from models that account for heteroskedasticity
```{r}
library(brms)

get_brms_models = function(dat,warm=5000,iter=10000,chains=4,cores=4){
  # Get null model - intercept only accounting for heteroskedasticity
  H0 = brm(formula=brms::bf(DFB~1,sigma~Ipast),data=dat,warm=warm,iter=iter,chains=chains,cores=cores,save_all_pars=T)
  
  # Get alternative model - predicts linear slope between optimality and complexity
  H1 = brm(formula=brms::bf(DFB~Ipast,sigma~Ipast),data=dat,warm=warm,iter=iter,chains=chains,cores=cores,save_all_pars=T)
  
  # Get bayes factor
  bayesF = brms::bayes_factor(H1,H0)
  
  # Return brms fit objects and bayes factor
  return(list(H0=H0,H1=H1,BF=bayesF$bf))
}

h1_fits = get_brms_models(subset(adat,Hazard=='H=0.01'))
h9_fits = get_brms_models(subset(adat,Hazard=='H=0.99'))
print('Done')
```
 Bayes factor shows clear null and alternative in low and high hazrd respectively
```{r}
print(paste('Evidence for correlation in Hazard = 0.01:',h1_fits$BF))
print(paste('Evidence for correlation in Hazard = 0.99:',h9_fits$BF))
```


Power analysis - since confirming a null requires more data than confirming an effect, lets examine how many subjects we would need to confirm a null in the low hazard rate condition using simulated subjects using the regression coefficients we indentified above

```{r}
# Function to simulate subject, fit null and alternative, and compute bayes factor
get_bf = function(nsub,m,b,sig_m,warm=5000,iter=10000,chains=4,cores=4){
  x = runif(nsub)
  y = sapply(1:length(x),function(j) rnorm(1,mean=m*x[j]+b,x[j]*sig_m))
  dat = data.frame(x=x,y=y)
  h0 = brm(formula=brms::bf(y~1,sigma~x),data=dat,warm=warm,iter=iter,chains=chains,cores=chains,save_all_pars=T)
  h1 = brm(formula=brms::bf(y~x,sigma~x),data=dat,warm=warm,iter=iter,chains=chains,cores=chains,save_all_pars=T)
  bayesf = bayes_factor(h1,h0)
  return(bayesf$bf)
}

# Get regression coefficients from null observed above (low hazard)
h1_reg = summary(h1_fits$H0)
h1_coefs = h1_reg$fixed[,1]
```

Here is where I do the actual simulation
```{r,echo=FALSE,message=FALSE}
nboot = 25 #Number of iterations
n = 60     #Number of subject
#bfs = readRDS(paste('./bfs_null_',n,'.rds'))
#bfs = c(bfs,sapply(1:nboot,function(i) get_bf(n,0,h1_coefs[[1]],exp(h1_coefs[[2]]+h1_coefs[[3]]))))
bfs = sapply(1:nboot,function(i) get_bf(n,0,h1_coefs[[1]],exp(h1_coefs[[2]]+h1_coefs[[3]])))
saveRDS(bfs,paste('./bfs_null_',n,'.rds'))
```

